### 2015-07-22 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:07:22	13:35:27	(Wed22.Jul)

\IEEEPARstart{D}{ata-driven} methods have been introduced in various imaging fields over the years in attempts to improve image quality. One such method is the minimum variance distortionless response (MVDR) beamformer. Compared to conventional methods, MVDR is often able to improve image contrast and resolution, as shown in~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}.

>>>>

\IEEEPARstart{A}{daptive} methods detector design is a term methods have been introduced in various imaging fields over the years in attempts to improve image quality. One such method is the minimum variance distortionless response (MVDR) beamformer. Compared to conventional methods, MVDR is often able to improve image contrast and resolution, as shown in~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}.

### 2015-07-22 ThesisJo/introduction.tex
la2pdf commit - 2015:07:22	13:35:27	(Wed22.Jul)

>>>>

C-I:

Introduction
   Beamforming
   Wave fields and Array Processing
   Conventional Beamforming
   Adaptive Beamforming
      MVDR
      Capon/MPDR
      APES
      Wiener
   Medical Ultrasound Imaging
   Medical Ultrasound Imaging
   Digital Beamforming
      Compact Beamformers & Delta Sigma
      Adaptive Beamforming in Medical Ultrasound Imaging
         MVDR-based Beamformers and Related Methods
         The Coherence Factor
         Other Adaptive Methods
Summary of publications
   Paper I-VII
Discussion and future work
   Summary and discussion
   Future Work

J-F:

Propagating Waves
Beamforming
  Beampattern
Minimum Variance Beamforming
  Signal Cancellation
  Robust Minimum Variance Beamforming
  Other Adaptive Methods
  Other High Resolution Methods
Medical Ultrasound Imaging
  Broadband Near Field Minimum Variance Beamforming
  Estimation of the Spatial Covarance Matrix
Adaptive Beamforming in Medical Ultrasound Imaging: State of the Art
Blind Source Separation
  Independent Component Analysis
  Relation to Adaptive Beamforming
Summary  of Papers
Discussion
Conclusion and further research

Ann:

Introduction
   Aims of the thesis
   Motivation and scope
   Outline
Background
   Sonar
      Historical Perspective
      Sonar Imaging
      Scattering and Reflection
      Key challenges
   Propagating sound waves
   Array processing and beamforming
      Signal model
      Conventional beamforming
      The beampattern
   Adaptive Beamforming
      Optimal MPDR and MVDR
      Adaptive MVDR
      Adaptive APES
      Low Complexity LCA
      Adaptive methods based on aperture coherence
      Robustness of adaptive beamformers
   Performance metrics
Summary of publications
Summary and Discussion
Future work

Wei:

Introduction
   Overview of fractional calculus
   Challenges of fractional calculus
   Definition of fractional calculus
   Fractional calculus and anomalous phenomena
      Non-Fourier heat conduction
      Modeling arbitrary power law attentuation
   Solving fractional differential equations
      Analytical methods
      Numerical models
   Optimization and parallelization
      Locality and data reuse
      Vectorization
      Parallelization
   Performance modeling
      Serial Performance model
      Parallel Performance model
Summary of papers
Future work

JP

Background
   General-purpose computing on GPUs
      Comparing CPU and GPy performance
      Programming a GPU
   Medical Ultrasound Imaging
      Beamforming
      Sampling and processing complexity
      GPUs in medical ultrasound imaging
      Adaptive beamforming
      Capon beamforming of focused broadband beams
   Volume rendering
      Adaptive volume rendering
   Ultrasound field simulations
   Concluding remarks
Introduction to papers
   Motivation
   Aims of study
   Summary of papers
   Main contributions
   Discussion and future work
   Multimedia content
   Software
References
Papers
